---
title: "FORMATIVE ASSESSMENT 6"
author: "Lindsy Rossel C. Masicat"
date: "2024-02-28"
output: html_document
---

## I. Geometric Distribution

### Provide an R code for the geometric distribution. The geometric distribution is a probability distribution that models the number of trials required to achieve the first success in a sequence of Bernoulli trials, where each trial has a constant probability of success.

+ 1. Set the probability of success
``` {r prob}    
    p <- 0.2
```

+ 2. Generate 1000 random variables from the geometric distribution.

``` {r gen}  

    rand_var <- 1000

    x <- rgeom(rand_var, p) + 1
    x
```

+ 3. Calculate some basic statistics:
<br> mean_x = mean
<br> var_x = variance
<br> sd_x = standard deviation

``` {r calc}

    mean_x <- mean(x)
    var_x <- var(x)
    sd_x <- sd(x)
    
```

+ Print the results in item 3 with the following output (string): 
  <br> Number of trials required to achieve first success:
  <br> Mean (in 2 decimal places):
  <br> Variance (in 2 decimal places):
  <br> Sandard deviation ( in 2 decimal places):

``` {r print}

    cat("Number of trials required to achieve first success: \n")
    cat("Mean (in 2 decimal places): ", round(mean_x, 2), "\n")
    cat("Variance (in 2 decimal places): ", round(var_x, 2), "\n" )
    cat("Standard deviation (in 2 decimal places): ", round(sd_x, 2), "\n")
    
```

+ Plot the histogram of the results.


```{r x, echo=FALSE}
hist(
  x, col = "blue", xlab = "Number of Trials", 
  main = "Results of Geometric Distribution"
)
```


## II. Hypergeometric Distribution.  
### Consider a plant manufacturing IC chips of which 10% are expected to be defective. The chips are packed in boxes for export. Before transportation, a sample is drawn from each box. Estimate the probability that the sample contains more than 10% defectives, when:

+ 1. A sample of 10 is selected from a box of 40;
```{r hypergeometric}
  
x <- 2:10
sample_drawn <- 10
sample_size <- 40
def_percent <- 0.1
num_def <- sample_size*def_percent

prob_1 <- dhyper(x, num_def, sample_size-num_def, sample_drawn)
prob_1
totalprob_1 <- sum(prob_1)

cat("The probability that the sample contains more than 10% defectives when 10 samples are drawn from a box of 40 is ", totalprob_1, "\n")

```
+ Plot for sample of 10 selected from a box of 40.
```{r plot 1}

  plot(x, prob_1,
  xlab = "Number of defectives", type = "h",
  ylab = "P(X = x)",
  main = "N = 40, M = 4, n = 10", font.main = 1)
```

+ 2. A sample of 10 is selected from a box of 5000.
```{r hypergeometric 2}
  
x <- 2:10
sample_drawn <- 10
sample_size <- 5000
def_percent <- 0.1
num_def <- sample_size*def_percent

prob_2 <- dhyper(x, num_def, sample_size-num_def, sample_drawn)
prob_2
totalprob_2 <- sum(prob_2)

cat("The probability that the sample contains more than 10% defectives when 10 samples are drawn from a box of 5000 is ", totalprob_2 , "\n")
```

+ Plot for sample of 10 selected from a box of 5000.
```{r plot 2}

  plot(x, prob_2,
  xlab = "Number of defectives", type = "h",
  ylab = "P(X = x)",
  main = "N = 5000, M = 500, n = 10", font.main = 1)
```